Create histogram with risk scores

### 2023-11-23 Code/0_PrepareValidationData.Rmd
Final commit

---
title: "Prepare Validation Data"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

Define recurrence time in years
```{r, eval=TRUE}
sel.val.data$Rec.time <- (sel.val.data$Date_1st_Rec-sel.val.data$SNdate)/(24*60*60)/365.25
```

Check: no patients with Rec date before SN date
```{r, eval=TRUE}
sum(!(!(sel.val.data$Rec.time<0&!is.na(sel.val.data$Rec.time))))
```

Set recurrence time equal to follow-up time for those without recurrence
```{r, eval=TRUE}
sel.val.data$Rec.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]<-sel.val.data$FU.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]

sel.val.data$Rec.time[sel.val.data$Recurrence=="recurrence"&is.na(sel.val.data$Date_1st_Rec)]<-NA
table(sel.val.data$Status, sel.val.data$Recurrence)
```

#### Melanoma specific mortality (MSM)
```{r, eval=TRUE}
sel.val.data$dead <- as.numeric(stringr::str_detect(sel.val.data$Status, "Dead"))
sel.val.data$dead <- factor(sel.val.data$dead, labels=c("No", "Yes"))
table(sel.val.data$Status, sel.val.data$dead)
sel.val.data$MSM <- as.numeric(sel.val.data$Status=="Dead, melanoma       ")
```
#### Mitosis
Define Mitosis as Yes/No
```{r, eval=TRUE}
sel.val.data$Mitosis <- as.numeric(sel.val.data$Mitosis)
```

@@

# Multiple imputation
```{r, eval=TRUE}
variables.to.be.imputed <- c("Center", "SNstatus", "Sex", "Age.SN", "Ulceration",
                             "Loc_CAT", "Histology", "Breslow", "multiple.fields",
                             "Tot_SNs_neg", "Tot_SNs_pos", "Rdamcrit", "Dewar",
                             "Mitosis", "Recurrence", "dead", "MSM")
validation.data.to.be.imputed <- sel.val.data[, variables.to.be.imputed]
```

Save distributions of all variables, necessary for Harrell summaries
```{r, eval=TRUE}
dd.validation<-rms::datadist(validation.data.to.be.imputed)
options(datadist="dd.validation")
options(digits=8)
```

Relation between outcome and covariates
```{r, eval=TRUE}
validation.data.to.be.imputed$logRec.time <- log(sel.val.data$Rec.time+1/365.25)
validation.data.to.be.imputed$logFU.time <- log(sel.val.data$FU.time+1/365.25)
missings.table(validation.data.to.be.imputed)
save(list=c("dd.validation", "validation.data.to.be.imputed"),file="Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata", compress=TRUE)
```

>>>>

---
title: "Prepare Validation Data"
author: "Carolien C.H.M. Maas"
date: "November 2023"
output: html_document
---

@@

Define recurrence time in years
```{r, eval=TRUE}
sel.val.data$Recurrence.time <- (sel.val.data$Date_1st_Rec-sel.val.data$SNdate)/(24*60*60)/365.25
```

Check: no patients with Rec date before SN date
```{r, eval=TRUE}
sum(!(!(sel.val.data$Recurrence.time<0&!is.na(sel.val.data$Recurrence.time))))
```
# Define death by any cause
```{r, eval=TRUE}
sel.val.data$dead <- as.numeric(stringr::str_detect(sel.val.data$Status, "Dead"))
sel.val.data$dead <- factor(sel.val.data$dead, labels=c("No", "Yes"))
``` 
<!-- Set recurrence time equal to follow-up time for those without recurrence -->
<!-- ```{r, eval=TRUE} -->
<!-- sel.val.data$Recurrence.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]<-sel.val.data$FU.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)] -->

<!-- sel.val.data$Recurrence.time[sel.val.data$Recurrence=="recurrence"&is.na(sel.val.data$Date_1st_Rec)]<-NA -->
<!-- table(sel.val.data$Status, sel.val.data$Recurrence) -->
<!-- ``` -->
Create composite Recurrence
```{r, eval=TRUE}
# event = 1 if recurrence or death, whichever occurs first
sel.val.data$Rec.composite <- ifelse(sel.val.data$Recurrence=="recurred" | sel.val.data$dead=="Yes", 1, 0)

# if patient has recurrence, set time to Recurrence.time
# if patient has no recurrence, but died, set time to FU.time
# if patient has no recurrence, and did not die, set to FU.time
sel.val.data$Rec.composite.time <- ifelse(sel.val.data$Recurrence=="recurred", 
       sel.val.data$Recurrence.time,
       sel.val.data$FU.time)
```
#### Melanoma specific mortality (MSM)
```{r, eval=TRUE}
table(sel.val.data$Status, sel.val.data$dead)
sel.val.data$MSM <- as.numeric(sel.val.data$Status=="Dead, melanoma       ")
```
#### Mitosis
Define Mitosis as Yes/No
```{r, eval=TRUE}
sel.val.data$Mitosis <- as.numeric(sel.val.data$Mitosis)
```

@@

Relation between outcome and covariates
```{r, eval=TRUE}
sel.val.data$logRec.composite.time <- log(sel.val.data$Rec.composite.time+1/365.25)
sel.val.data$logFU.time <- log(sel.val.data$FU.time+1/365.25)
```

# Multiple imputation
```{r, eval=TRUE}
variables.to.be.imputed <- c("Center", "SNstatus", "Sex", "Age.SN", "Ulceration",
                             "Loc_CAT", "Histology", "Breslow", "multiple.fields",
                             "Tot_SNs_neg", "Tot_SNs_pos", "Rdamcrit", "Dewar",
                             "Mitosis", "Status",
                             "Rec.composite", "logRec.composite.time", 
                             "MSM", "logFU.time")
validation.data.to.be.imputed <- sel.val.data[, variables.to.be.imputed]
missings.table(validation.data.to.be.imputed)
```

Save distributions of all variables, necessary for Harrell summaries
```{r, eval=TRUE}
dd.validation<-rms::datadist(validation.data.to.be.imputed)
options(datadist="dd.validation")
options(digits=8)
save(list=c("dd.validation", "validation.data.to.be.imputed"),file="Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata", compress=TRUE)
```

### 2023-11-23 Code/12_Validation.Rmd
Final commit

---
title: "Create histogram with risk scores"
author: "Carolien C.H.M. Maas"
date: "December 2022"
output: html_document
---

@@

# Training data
```{r, eval=TRUE}
# load model
load("Z:/Project Melanoom/PaperMelanoma/Results/h0.Rec.MSM.Rdata")

# load data
load("Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.RData")

@@

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".All.png"))
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p, S,
                                 g=5,main="All patients", time=NULL,lim=c(0,1),dist=TRUE)
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Positive.png"))
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Positive",],
                                 S[data$SNstatus=="Positive",],
                                 g=5,main="Patients with positive SN", time=NULL,lim=c(0,1),dist=TRUE)
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Negative.png"))
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Negative",],
                                 S[data$SNstatus=="Negative",],
                                 g=5,main="Patients with negative SN", time=NULL,lim=c(0,1),dist=TRUE)
    grDevices::dev.off()

>>>>

---
title: "Validate model"
author: "Carolien C.H.M. Maas"
date: "November 2023"
output: html_document
---

@@

# Training data
```{r, eval=TRUE}
# load data
load("Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.RData")

@@

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".All.png"))
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p, S,
                                 g=5, main="All patients", time=NULL, 
                                 lim=c(0,1), dist=TRUE,
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Positive.png"))
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Positive",],
                                 S[data$SNstatus=="Positive",],
                                 g=5, main="Patients with positive SN", 
                                 time=NULL, lim=c(0,1), dist=TRUE,
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", data.type, ".", outcome, ".Negative.png"))
    par(mar=rep(0, 4))
    PredictionTools::val.surv.mi(p[data$SNstatus=="Negative",],
                                 S[data$SNstatus=="Negative",],
                                 g=5, main="Patients with negative SN", 
                                 time=NULL, lim=c(0,1), dist=TRUE,
                                 optimism.C=ifelse(data.type=="training", optimism, 0))
    grDevices::dev.off()

### 2023-11-23 Code/5_FitModels.Rmd
Final commit

---
title: "Fit models and plots"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

# Calibrated final model for melanoma specific mortality
Fit disease specific mortality to the linear predictor of recurrence
```{r, eval=TRUE}
# Combine calibration coefficients for all imputated data sets 
MSM.cal.fact.all <- c()
MSM.cal.fact.SE <- c()
for (i in 1:m){
  lp.i<-predict(f.mi.BS.Rec.5,
                newdata=mice::complete(imputed.training.data,i), 
                type="lp")
  f.mi.i <- rms::cph(S.MSM.5.training~lp.i,y=TRUE,x=TRUE) 
  MSM.cal.fact.all <- c(MSM.cal.fact.all, stats::coef(f.mi.i))
  MSM.cal.fact.SE <- c(MSM.cal.fact.SE, sqrt(diag(vcov(f.mi.i))))
}
MSM.cal.fact.combined<-Rubin.combine(MSM.cal.fact.all, MSM.cal.fact.SE)
MSM.cal.fact <- MSM.cal.fact.combined$est

@@

# c-index
p.MSM.5.redev<- matrix(NA, nrow(training.data.to.be.imputed), m)
f.MSM.basehaz <- survival::basehaz(cph(form.full.MSM.5.redev, 
                             data=mice::complete(imputed.training.data, 1), 
                             se.fit=TRUE, x=TRUE, y=TRUE))
h0.MSM.redev <- f.MSM.basehaz$hazard[f.MSM.basehaz$time==max(f.MSM.basehaz$time[f.MSM.basehaz$time<=horizon])]
for (i in 1:m){
  lp.val.i <- predict(f.mi.full.MSM.5.redev,
                      newdata=mice::complete(imputed.training.data, i),
                      type="lp")
  p.MSM.5.redev[, i] <- 1-exp(-h0.MSM.redev*exp(lp.val.i))
}
PredictionTools::val.surv.mi(p.MSM.5.redev, S.MSM.5.training, g=5,
                             main="All patients",time=NULL,lim=c(0,1),dist=TRUE)
```

>>>>

---
title: "Fit models and plots"
author: "Carolien C.H.M. Maas"
date: "November 2023"
output: html_document
---

@@

# Calibrated final model for melanoma specific mortality
Fit disease specific mortality to the linear predictor of recurrence
```{r, eval=TRUE}
# Combine calibration coefficients for all imputated data sets 
MSM.cal.fact.all <- c()
MSM.cal.fact.SE <- c()
for (i in 1:m){
  lp.i<-predict(f.mi.BS.Rec.5,
                newdata=mice::complete(imputed.training.data,i), 
                type="lp")
  f.mi.i <- rms::cph(S.MSM.5.training~lp.i,y=TRUE,x=TRUE) 
  MSM.cal.fact.all <- c(MSM.cal.fact.all, stats::coef(f.mi.i))
  MSM.cal.fact.SE <- c(MSM.cal.fact.SE, sqrt(diag(vcov(f.mi.i))))
}
MSM.cal.fact.combined <- Rubin.combine(MSM.cal.fact.all, MSM.cal.fact.SE)
MSM.cal.fact <- MSM.cal.fact.combined$est

@@

# c-index
p.MSM.5.redev<- matrix(NA, nrow(training.data.to.be.imputed), m)
f.MSM.basehaz <- survival::basehaz(cph(form.full.MSM.5.redev, 
                             data=mice::complete(imputed.training.data, 1), 
                             se.fit=TRUE, x=TRUE, y=TRUE))
h0.MSM.redev <- f.MSM.basehaz$hazard[f.MSM.basehaz$time==max(f.MSM.basehaz$time[f.MSM.basehaz$time<=horizon])]
for (i in 1:m){
  lp.val.i <- predict(f.mi.full.MSM.5.redev,
                      newdata=mice::complete(imputed.training.data, i),
                      type="lp")
  p.MSM.5.redev[, i] <- 1-exp(-h0.MSM.redev*exp(lp.val.i))
}
PredictionTools::val.surv.mi(p.MSM.5.redev, S.MSM.5.training, g=5,
                             main="All patients", time=NULL, lim=c(0, 1),
                             dist=TRUE)
```

### 2023-11-23 Code/6_CreateTablesandPlots.Rmd
Final commit

---
title: "Create Tables"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

# load libraries
library(foreign)
library(mice)
library(survminer)
library(prodlim)
library(rms)
library(Hmisc)
library(png)
library(PredictionTools)
source("Z:/Project Melanoom/PaperMelanoma/Code/PaperMelanomaFunctions.R")
```

@@

# Calculate optimism using bootstrap using full model and doing backward selection for each bootstrap
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(100)
slope<-NULL
cindex.orig<-NULL
opt<-NULL
cindex.B<-NULL
for (i in 1:m){
  v<-validate(f.mi.full.Rec.5$fits[[i]],method="boot",bw=TRUE,rule="p",sls=0.05,B=100,pr=FALSE,type="individual")
  slope<-c(slope,v["Slope","test"]) # slope of test
  cindex.orig<-c(cindex.orig,(v["Dxy","index.orig"]+1)/2) # original C-index
  opt<-c(opt,v["Dxy","optimism"]/2) # optimism C-index
  cindex.B<-c(cindex.B,(v["Dxy","index.corrected"]+1)/2) # index corrected C-index
}
```

@@

CIndex.Rec.Table <- rbind(CIndex.BS.Rec.5.All, CIndex.BS.Rec.5.Positive, CIndex.BS.Rec.5.Negative)
CIndex.Rec.Table
utils::write.table(CIndex.Rec.Table,
              file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/CIndex.train.txt"),
              row.names=FALSE, col.names=FALSE, sep=",")
```

>>>>

---
title: "Create Tables"
author: "Carolien C.H.M. Maas"
date: "November 2023"
output: html_document
---

@@

# load libraries
library(foreign)
library(mice)
library(survminer)
library(prodlim)
library(rms)
library(Hmisc)
library(png)
# remotes::install_github("CHMMaas/PredictionTools")
library(PredictionTools)
source("Z:/Project Melanoom/PaperMelanoma/Code/PaperMelanomaFunctions.R")
```

@@

# Calculate optimism using bootstrap using full model and doing backward selection for each bootstrap
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(100)
slope<-NULL
cindex.orig<-NULL
opt<-NULL
cindex.B<-NULL
for (i in 1:m){
  v <- validate(f.mi.full.Rec.5$fits[[i]], method="boot", bw=TRUE, rule="p",
                sls=0.05, B=100, pr=FALSE, type="individual")
  slope <- c(slope, v["Slope","test"]) # slope of test
  cindex.orig <- c(cindex.orig, (v["Dxy","index.orig"]+1)/2) # original C-index
  opt <- c(opt, v["Dxy","optimism"]/2) # optimism C-index
  cindex.B <- c(cindex.B, (v["Dxy","index.corrected"]+1)/2) # index corrected C-index
}
```

@@

CIndex.Rec.Table <- rbind(CIndex.BS.Rec.5.All, CIndex.BS.Rec.5.Positive, CIndex.BS.Rec.5.Negative)
CIndex.Rec.Table
utils::write.table(CIndex.Rec.Table,
              file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/CIndex.train.txt"),
              row.names=FALSE, col.names=FALSE, sep=",")

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

### 2023-11-23 Code/7_CreateCrossValidatedCalibrationPlots.Rmd
Final commit

---
title: "Create calibration plots"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

# load libraries
library(Hmisc)
library(survival)
library(rms)
library(mice)
library(grDevices)
source("Z:/Project Melanoom/PaperMelanoma/Code/PaperMelanomaFunctions.R")
# remotes::install_github("CHMMaas/PredictionTools")
library(PredictionTools)  # to plot calibration
```

>>>>

---
title: "Create calibration plots"
author: "Carolien C.H.M. Maas"
date: "November 2023"
output: html_document
---

@@

# load libraries
library(Hmisc)
library(survival)
library(rms)
library(mice)
library(grDevices)
# remotes::install_github("CHMMaas/PredictionTools")
library(PredictionTools)  # to plot calibration
source("Z:/Project Melanoom/PaperMelanoma/Code/PaperMelanomaFunctions.R")
```

### 2023-11-23 Code/9_CreateRiskScoreHistogram.Rmd
Final commit

---
title: "Create histogram with risk scores"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

# lp range MSM
rc.MSM <- MSM.cal.fact*rc.Rec
int.MSM <- MSM.cal.fact*int.Rec
max.range <- 16
points.range <- 0:max.range
lp.points.Rec.5 <- int.Rec+rc.Rec*points.range
lp.points.MSM.5 <- int.MSM+rc.MSM*points.range

# Recurrence lp scores
Breslow.trunc <- last.imputed.training.data.set$Breslow
Breslow.trunc[last.imputed.training.data.set$Breslow<0.1] <- .1
Breslow.trunc[last.imputed.training.data.set$Breslow>7] <- 7
lp.Rec <- predict(f.mi.BS.Rec.5,newdata=data.frame(SNstatus=last.imputed.training.data.set$SNstatus,
                                                         Age.SN=last.imputed.training.data.set$Age.SN,
                                                         Ulceration=last.imputed.training.data.set$Ulceration,
                                                         Loc_CAT=last.imputed.training.data.set$Loc_CAT,
                                                         Breslow=Breslow.trunc,
                                                         Rdamcrit=last.imputed.training.data.set$Rdamcrit))
mean(lp.Rec)
score.Rec <- round((lp.Rec-int.Rec)/rc.Rec,0)
max.breaks <- max.range+1
h.Rec <- hist(score.Rec,plot=FALSE,breaks=0:max.breaks,right=FALSE, beside=TRUE)

@@

save(h0.Rec, h0.MSM, coef.Rec, c.Breslow, center.Rec, MSM.cal.fact,
     file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/h0.Rec.MSM.Rdata"), compress=TRUE)
save(list=c("dd.training", "training.data.to.be.imputed", "m", "imputed.training.data", 
            "last.imputed.training.data.set", "horizon", "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", 
            "form.full.Rec.5", "form.BS.Rec.5", "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec", "lp.points.Rec.5",
            "rc.MSM", "rc.Rec", "h0.MSM", "lp.points.MSM.5",
            "lp.Rec", "lp.MSM", "max.breaks", "h.Rec", 
            "h.plot", "y.lim.hist", "x.lim", "coef.Rec", "center.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

>>>>

---
title: "Create histogram with risk scores"
author: "Carolien C.H.M. Maas"
date: "November 2023"
output: html_document
---

@@

# lp range MSM
rc.MSM <- MSM.cal.fact*rc.Rec
int.MSM <- MSM.cal.fact*int.Rec
max.range <- 17
points.range <- 0:max.range
lp.points.Rec.5 <- int.Rec+rc.Rec*points.range
lp.points.MSM.5 <- int.MSM+rc.MSM*points.range

# Recurrence lp scores
Breslow.trunc <- last.imputed.training.data.set$Breslow
Breslow.trunc[last.imputed.training.data.set$Breslow<0.1] <- .1
Breslow.trunc[last.imputed.training.data.set$Breslow>7] <- 7
lp.Rec <- predict(f.mi.BS.Rec.5,newdata=data.frame(SNstatus=last.imputed.training.data.set$SNstatus,
                           Age.SN=last.imputed.training.data.set$Age.SN,
                           Ulceration=last.imputed.training.data.set$Ulceration,
                           Loc_CAT=last.imputed.training.data.set$Loc_CAT,
                           Breslow=Breslow.trunc,
                           Rdamcrit=last.imputed.training.data.set$Rdamcrit))
mean(lp.Rec)
score.Rec <- round((lp.Rec-int.Rec)/rc.Rec, 0)
max.breaks <- max.range+1
h.Rec <- hist(score.Rec, 
              plot=FALSE,
              breaks=0:max.breaks,
              right=FALSE, 
              beside=TRUE)

@@

save(rc.Rec, int.Rec, f.mi.BS.Rec.5, MSM.cal.fact, max.range,
     file="Z:/Project Melanoom/PaperMelanoma/Results/model.Rdata", 
     compress=TRUE)

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", 
            "f.mi.full.MSM.5.refit", "f.mi.BS.MSM.5.refit", 
            "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec", "lp.points.Rec.5",
            "rc.MSM", "rc.Rec", "h0.MSM", "lp.points.MSM.5",
            "lp.Rec", "lp.MSM", "max.breaks", "h.Rec",
            "h.plot", "y.lim.hist", "x.lim", "coef.Rec", "center.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```
